\begin{thebibliography}{99}

\bibitem{sethian97}
	James A. Sethian,
	\emph{Level Set Methods: An Act of Violence}.
	1997.

\bibitem{osher88}
	S. Osher \& James A. Sethian,
	\emph{Fronts propagating with curvature-dependent speed: algorithms based on hamilton-jacobi formulation}.
	Journal of computational physics 79.1,
	1988.
\bibitem{adalsteinsson94}
	David. Adalsteinsson \& James A. Sethian,
	\emph{A fast level set method for propagating interfaces}.
	Journal of Computational Physics,
	1994.

\bibitem{osher02}
	Stanley Osher \& Ronald Fedkiw,
	\emph{Level set methods and dynamic implicit surfaces}.
	Vol. 153. Springer,
	2002.

\bibitem{mulder92}
	W. Mulder \& S. Osher \& James A. Sethian,
	\emph{Computing interface motion in compressible gas dynamics}.
	Journal of Computational Physics 100.2,
	1992.

\bibitem{whitaker89}
	Ross T. Whitaker,
	\emph{A level-set approach to 3D reconstruction from range data}.
	International Journal of Computer Vision 29.3,
	1998.

\bibitem{lefohn04}
	Aaron E. Lefohn \& Joe M. Kniss \& Charles D. Hansen \& Ross T. Whitaker,
	\emph{A streaming narrow-band algorithm: Interactive computation and visualization of level sets}.
	IEEE Transactions on Visualization and Computer Graphics,
	2004.

\bibitem{cates03}
	Aaron E. Lefohn \& Joshua Cates \& Ross T. Whitaker,
	\emph{Interactive, GPU-based level sets for 3D segmentation}.
	 Medical Image Computing and Computer-Assisted Intervention,
	2003.


\bibitem{drung00}
	Dzung L. \& Chenyang Xu \& Jerry L. Prince, 
	\emph{A Survey of Current Methods in Medical Image Segmentation}.
	Annual review of biomedical engineering 2.1,
	2000.

\bibitem{torsten05}
	T. Rohlfing \& R. Brandt \& R. Menzel \& Daniel B. Russakoff \& Calvin R. Mauer,
	\emph{Quo Vadis, Atlas-Based Segmentation?}.
	Handbook of Biomedical Image Analysis, pp. 435-438,
	2005.	

\bibitem{josein03}
	Josien P. W. Pluim \& J. B. Antoine Maintz \& Max A. Viergever,
	\emph{Mutual-information-based registration of medical images: a survey}.
	Medical Imaging, IEEE Transactions, pp. 986-1004,
	2003.
	
	
%\bibitem{}
%	authors,
%	\emph{}.
%	bla,
%	1999999.

%\bibitem{}
%	authors,
%	\emph{}.
%	bla,
%	1999999.
	
%\bibitem{}
%	authors,
%	\emph{}.
%	bla,
%	1999999.

\end{thebibliography}
